\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
planning

For our project, we are using a collection of data from the StarPlus project\footnote{StarPlus project - http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-81/www/}. This dataset contains the results from a trial experiment performed at Carnegie Mellon University. The data was originally collected my Marcel Just \textit{et al}.

The dataset contains data on 6 test subjects that each completed a number of trials. For each trial (see section \ref{sec:setup}), 54 fMRI snapshots were made of specific regions of their brain. Each snapshot consists of a list of 3d pixels (so called voxels). The dimensions of these snapshots are 64x64x8 voxels, amounting to a total of 5700 voxels per snapshot (this is less than 64 * 64 * 8 because only specific regions were recorded).

@@

\begin{description}
	\item[11th - 21st September]\-\\
	Research ...
	\item[22nd - 28th September]\-\\
	Model definition ...
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	Preparing the presentation ...
	\item[28th October]\-\\
	Final delivery of the document and the implementation
\end{description}

>>>>

For our project, we are using a collection of data from the StarPlus project\footnote{StarPlus project - http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-81/www/}. This dataset contains the results from a trial experiment performed at Carnegie Mellon University. The data was originally collected by Marcel Just \textit{et al}.

The dataset contains data on 6 test subjects that each completed a number of trials. For each trial (cf. Section~\ref{sec:setup}), 54 fMRI snapshots were made of specific regions of their brain. Each snapshot consists of a list of 3d pixels (so called voxels). The dimensions of these snapshots are 64x64x8 voxels, amounting to a total of 5700 voxels per snapshot (this is less than 64 * 64 * 8 because only specific regions were recorded).

@@

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the model will be realised. 
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation ...
	\item[20th - 22nd October]\-\\
	Preparing the presentation ...
	\item[28th October]\-\\
	Final delivery of the document and the implementation
\end{description}
